XXX

### 2012-03-25 paper/engNERwiki.tex
Evaluation is kesz

The full mapping can be found in Appendix~\ref{sec:appa}.

@@

For the English cross-corpus evaluation the CoNLL-2003 dataset was chosen, mostly because of the similarity in tagset and format. It is well-studied (e.g. XXX) that cross-checking between different corpora does not lead to F-measure improvement. Stylistic and domain differences certainly affect NER performance, and the different annotation schemes pose several compatibility problems. Nothman et al.~\shortcite{Nothman:08} showed that each set of gold standard training data performs much better on corresponding test sets than on test sets from other sources. The situation here is similar: the NE-tagger trained on Wikipedia does not achieve as high performance tested against CoNLL test set as one trained on the own training set (see table \ref{enresults} and \ref{huresults} for results).

@@

Results of experiments done on the Hungarian corpus look similar.

Although two human-annotated NER corpora exist for Hungarian, we chose the Szeged NER corpus \cite{}, which follows the CoNLL annotation scheme. It contains ca.

The strong correlation between capitalization and named entities makes recognition of entities in text relatively simple: a word is part of an entity if it is capitalized.

training corpora in absence of gold standard datasets

training sets for domains differing from newswire

@@

\bibitem[\protect\citename{Balasuriya \bgroup et al.\egroup}2009]{Balasuriya:09}
Dominic Balasuriya, Nicky Ringland, Joel Nothman, Tara Murphy, James R. Curran
\newblock 2009.
\newblock Named Entity Recognition in Wikipedia.
\newblock In: {\em Proceedings of the 2009 Workshop on the People's Web Meets NLP, ACL-IJCNLP}, pages 10--18.

>>>>

%The full mapping can be found in Appendix~\ref{sec:appa}.

@@

For the English cross-corpus evaluation the CoNLL-2003 dataset was chosen, mostly because of the similarity in tagset and format. It is well-studied that cross-checking between different corpora leads to F-measure decrease. Stylistic and domain differences certainly affect NER performance, and the different annotation schemes pose several compatibility problems. Nothman et al.~\shortcite{Nothman:08} showed that each set of gold standard training data performs much better on corresponding test sets than on test sets from other sources. The situation here is similar: the NE-tagger trained on Wikipedia does not achieve as high performance tested against CoNLL test set as one trained on the own training set (see table \ref{enresults} for results).

@@

Since in the subtask of NE labeling for Hungarian we followed the Szeged NER corpus annotation guidelines, it is obvious to perform the experiments on this dataset, as well. Hungarian results are quite similar to the English ones (see table \ref{huresults}), the only difference is that F-measures for Hungarian are significantly higher, than ones for English. It can be due to the fact that the MISC category for Hungarian contains less types of names, thus the inconsistency and diversity of this class is smaller (see section \ref{sec:hun}). In contrast to the CoNLL corpus, the Szeged NER corpus was highly accurately annotated with an inter-annotator agreement over 99\%.

Due to the quite good F-measure of training on the Hungarian Wikipedia train corpus and testing on the corresponding test set, our Hungarian corpus can serve as a training corpus to build NE-taggers for domains falling out of newswire.

@@

%\bibitem[\protect\citename{Balasuriya \bgroup et al.\egroup}2009]{Balasuriya:09}
%Dominic Balasuriya, Nicky Ringland, Joel Nothman, Tara Murphy, James R. Curran
%\newblock 2009.
%\newblock Named Entity Recognition in Wikipedia.
%\newblock In: {\em Proceedings of the 2009 Workshop on the People's Web Meets NLP, ACL-IJCNLP}, pages 10--18.
